\section{Settings/Fundamental concepts}
The story is set in the Upside-Down, a dimension parallel to ours, in which there is little light and everything is covered with organic matter.
The starting point is Hawkins, a small town in Texas, where there is a school and a library. The city is surrounded by a forest, called Mirkwood, at the center of which is the energy laboratory, connected by drains to Lake Hawkins. Crossing the Old Sabine Wildlife you can reach Lindale, home of the museum. Far more distant is instead Dallas, the only fortified city not covered by organic matter. Finally, using an underground tunnel, you reach Fort Worth, now in ruins and a creature's lair.

The following laws, theories and concepts that govern the dimension of the Upside-Down will be explained by characters and/or documents within the game.

\begin{itemize}
	\item Time and Space: The Upside-Down is an alternative dimension that has the same characteristics and the same physical structures as our reality, but covered with organic material. It is therefore possible to hypothesize that this mass is produced by an organism that extends over an extremely large area, if not all over the globe. This non-sentient creature, called Upside-Down Core, has the Chronokinesis, a skill that allows it to replicate the structure of our reality at a given instant of time and apply it to the Upside-Down. This process takes place with a fixed and 
	continuous cadence, but only in the areas in which its organic matter extends.
	\item Dimensional Travel: when a person with high kinetic abilities abuses his power, there is the possibility that he does not die but is transported to the Upside Down. Here, with the exception of fortuitous cases or particular abilities, it remains trapped there without the possibility of escape.
	\item Demons: Except for the DemoGorgon with which Eleven had come into contact, no other demon has the ability to open gaps between dimensions.
\end{itemize}

