\section{Synopsis}

The death of the DemoGorgon, killed by Eleven, starts a paradox that, in addition to carrying the girl in the Upside-down, generates a reincarnation of 
the demon in the form of El herself, called B.A.D. Eleven (Biological Altered Demon \#011), having the same memories and abilities as the original.

\subsection{Act I}
BAD Eleven (Elby for short) wakes up in Hawkins school, confused and scared. Wandering through the building, she sees Eleven escaping through a portal, but later, after trying to get in, discovers that she can't cross it. Escaped from the library, she meets in the courtyard Kyle, a survivor of the Upside-Down, who leads her to his shelter. Here, after having taught her the basics of survival, he suggests that she should go to the laboratory to escape from the Upside-Down through the portal opened by Eleven.\\
Elby then walks towards the structure, but once she reaches the gap, she again fails to cross it. While heading for the exit,she finds the data and photos of projects \#003, \#005 and \#009. Back at the shelter, she uses her telekinesis to locate the three numbers and decides to go looking for \#005, while Kyle will meet \#003.\\
After crossing the Old Sabine Wildlife, Elby reaches Lindale and, inside the museum, meets \#005. The latter, after listening to the story of the girl, decides to follow her as interested in the portal.\\
Elby and \#005 return to the shelter, where he begins to become suspicious of the identity of Kyle. Having no further clues about the portal 
crossing method, they decide to leave for Dallas to meet \#009. Meanwhile Kyle managed to find \#003.

\subsection{Act II}
Arriving in Dallas, Elby and \#005 meet \#009 and \#010, who welcome them inside their hiding place. After several days of assignments, Dallas comes
attacked by a horde of monsters. Kyle takes advantage of the chaos generated by the clash to kidnap \#005. The true identity of Kyle is then revealed: he is \#001, the first experiment.\\
Elby and \#010 then start in pursuit of \#001, reaching the Giant Chasm.\\
Reached the Upside-Down Core, Elby and \#010 are captured by \#001 and assist while he kills \#005 and extracts its powers through the use of a parasite.
Having now both the biocynesis and the mental synchronization with the demons, \#001 is able to take control of the Core and use its chronocynesis at will.
Threatening to kill \#010, he forces Elby to open a portal, thus completing his plan to return home in the time instant he craves.

\subsection{Act III}
It is revealed that this is another alternative reality, and that it is therefore impossible to recreate the conditions to have the correct time and space. This causes a psychological breakdown in \#001, which kills \#010 and uses its powers to create a giant creature for the purpose of transporting the Core and expanding the Upside-Down to all realities, starting with that he came from.\\
Back in Dallas, along with a desperate \#009, Elby manages to break down the DemoWalker, allowing her to reach \#001 hidden inside. Here, aftera last exchange of ideals, the last battle takes place.\\
After the final battle, which foresees the death of all the surviving numbers, it is possible to see the Upside-Down Core, still active, while incorporatingthe corpses of \#001 and BAD Eleven. This causes a mutation in the creature, which takes shape of a giant spider and becomes a sentient entity, later called Mind Flayer. Reference is therefore made to the will of the demon to invade other dimensions (influence of \#001) and to the hatred it feels towards Eleven (influence of BAD Eleven), characteristics seen in the Second and Third Season.
